Modelling the Trojan Asteroids

### 2020-04-27 Report/draft1.tex
adapted planet_mass_variation

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/wanderwithplanetmass_p6}
	\caption{Variation of maximum wander with planetary mass, under a 0.01 AU radial perturbation and 0.01 AU/year tangential boost. Note the orbit stability up to $ M_{p} = 0.04 M_{s}$, and instability beyond this.}
	\label{fig:planetmass}
\end{figure}

An approximate quadratic trend is initially observed in the small mass region, with minimum wander occurring at $ M_{p} = 0.026 M_{s}$. However, the variation of wander below $ M_{p} = 0.04 M_{s}$ is minimal, while orbits are unstable beyond this point, in agreement with theoretical predictions by Darwin \cite{Darwin1897}.

\section{Conclusion}
This report demonstrates the stability of Lagrange points L\subscript{4} and L\subscript{5}, with a maximum deviation from the Lagrange points of $4.68 \times 10^{-13}$ AU over 1000 orbits (11,852 years), in a frame rotating with the asteroids and without perturbations applied. Stability under perturbations in both the XY plane and in the Z direction is also demonstrated, with a finite wander from these points independent of orbit duration. It was possible to further quantify this wander, suggesting a strong quadratic dependence on radial perturbation magnitude and independence of tangential perturbations, which did not grow beyond the initial perturbation size.
It was also possible to replicate both tadpole and horseshoe orbits from radial perturbations, and frequency components were obtained for these orbits in agreement with previous literature. It was also found that orbits become unstable when the planetary\textendash solar mass ratio is greater than 0.04, in agreement with theoretical predictions, and there is little mass dependence below this point.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/wanderwithplanetmass_q7}
	\caption{Variation of maximum wander with planetary mass, under a 0.001 AU radial perturbation and 0.001 AU/year tangential boost. Note the tendency }
	\label{fig:planetmass}
\end{figure}

For small planetary masses (up to approximately $ M_{p} = 0.01 M_{s}$), the wander follows a $ M_{P}^{-\frac{1}{2}}$ dependence, tending towards the initial perturbation for larger masses. However, wander increases unbounded and orbits become unstable beyond $ M_{p} = 0.04 M_{s}$, as depicted in Figure \ref{fig:planetmass2}, in agreement with theoretical predictions by Darwin \cite{Darwin1897}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/wanderwithplanetmass_p6}
	\caption{Variation of maximum wander with planetary mass, under a 0.01 AU radial perturbation and 0.01 AU/year tangential boost. Note the orbit stability up to $ M_{p} = 0.04 M_{s}$, and instability beyond this.}
	\label{fig:planetmass2}
\end{figure}

\section{Conclusion}
This report demonstrates the stability of Lagrange points L\subscript{4} and L\subscript{5}, with a maximum deviation from the Lagrange points of $4.68 \times 10^{-13}$ AU over 1000 orbits (11,852 years), in a frame rotating with the asteroids and without perturbations applied. Stability under perturbations in both the XY plane and in the Z direction is also demonstrated, with a finite wander from these points independent of orbit duration. It was possible to further quantify this wander, suggesting a strong quadratic dependence on radial perturbation magnitude and independence of tangential perturbations, which did not grow beyond the initial perturbation size.
It was also possible to replicate both tadpole and horseshoe orbits from radial perturbations, and frequency components were obtained for these orbits in agreement with previous literature. It was also found that orbits become unstable when the planetary\textendash solar mass ratio is greater than 0.04, in agreement with theoretical predictions, and inverse root mass dependence below this point.
